Contextual Combinatorial Cascading Bandits

### 2016-01-31 contextual combinatorial cascading bandits.tex
update until discussion

% my settings
\usepackage{amssymb,amsfonts,amsmath,bbm}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{empheq}
\usepackage{algorithm,algorithmic}
\usepackage{multirow}
\usepackage{ifthen}
\usepackage[usenames]{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{epstopdf}
%\usepackage{epsfig}
%\usepackage{times}
%\usepackage{helvet}
%\usepackage{courier}
%\usepackage{graphicx,subfigure}
%\usepackage{pdfpages}
%\usepackage{multirow}
%\usepackage{multicol}
\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\II}{\mathbb{I}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bOne}{\mathbbm{1}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bB}{\mathbf{B}}
\newcommand{\bO}{\mathbf{O}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand{\trace}{\mathrm{trace}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\| #1 \|}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}
\newtheorem{proposition}[theorem]{Proposition}%[chapter]
\newtheorem{definition}[theorem]{Definition}%[chapter]
\newtheorem{corollary}[theorem]{Corollary}%[chapter]
\newtheorem{lemma}[theorem]{Lemma}%[chapter]
\newtheorem{example}[theorem]{Example}
\newenvironment{proof}{\noindent {\textbf{Proof. }}}{$\Box$ \medskip}

\newcommand{\CLemmaPrefixExi}{
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
	$$
	p_{t, B} \geq \frac{1}{2}f_{t}^{\ast} - 1 + \gamma_{\abs{B}}, \qquad R(t, B) \geq \frac{1}{2} R(t, A).
	$$ 
}
\newcommand{\CEqDeltaEstAnd}{
	$$
	\EE_t [R(t, \bA_t) ] \leq \frac{8}{f^{\ast}} \EE_t \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} \right].
	$$
}
\newcommand{\CLemmaSumXiEstimateInDet}{
  If $\lambda \geq C_\gamma$, then
  $$
    \sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
  $$
}
\newcommand{\CLemmaDetVt}{
  $\det(\bV_t)$ is increasing with respect to $t$ and 
  $$
    \det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
  $$
}

@@

Putting context, position discounts, and generalized reward function together, we call
	our learning model the {\it contextual combinatorial cascading bandits}. 
We formally define this model, provide a complete algorithm and its regret analysis,
	and conduct experiments on both synthetic and real-world recommendation
	and network routing datasets to validate our approach.

The main contributions of this paper can be summarized as follows: (1) we propose a general framework  that incorporates contextual information,
position discounts, and general reward function to cover many real-world application scenarios; 
(2) we propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) we evaluate this algorithm on synthetic 
	and real-world datasets and the results show that our algorithm effectively
	incorporates contextual information and position discounts with significant performance gains.

\wei{The last two paragraphs have some repetition. 
	Is there any technical part in the algorithm and analysis that we would like to 
	mention in the introduction? So far the intro is only about conceptual additions to the model,
	and nothing about technical challenges and our solution. 
	It is ok if conceptual contribution is what we want to emphasize, but if there is any
	technical contribution we can say, we can also say it here.}

\shuai{Our proofs build on previous work but also generalize their proof in our setting. Two challenges have been dealt with, partial observability on contextual bandits and general reward function with position discounts.  }

@@

\wei{I revised the table, including adding a column about general reward, to match the introduction.}

@@

\wei{I removed all references to "weight" so far. I think it is a bit unclear and could be confusing.}

The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference comes first) has a better performance than in decreasing order of their UCBs.
This unnatural result is perhaps because the order of items does not affect the reward and thus
	putting low preference items first and high preference items last may result in more feedbacks
	in the cascade.
The position discounts introduced in this paper forces the recommended set in the decreasing order 
	of UCBs, which is more realistic.
The work of \cite{combes2015learning} considered a similar recommendation model of cascading bandits with position discounts, where all users are characterized into different classes and each item has a class-specific "reward". 
\wei{So, does that mean \cite{combes2015learning}, comparing to ours, only lacks of contextual
	information? or it our reward function is also more general? It is not very clear to me.}
\shuai{They dealt with discounted 'or' reward. At each time, suppose the user is from class $c$, then recommending her with $K$ items from item-class $h(c)$. We have more general reward function and more general context information.}
In our setting, users and items are represented by general feature vectors.
Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward. The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time. A recent work \cite{qin2014contextual} (refered to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward. Their feedback is more informative than ours. We relax the feedback from semi-bandit to cascading, yet our algorithm achieves the same order of regret bound.

@@

\wei{please cite the arxiv version below}
\citet{chen2015combinatorial} consider general reward functions and probabilistic triggering of base arms
	in the  stochastic combinatorial semi-bandit model (refered to as 'CUCB' in Table \ref{table:outline}).
Cascading bandits can be viewed as a particular type of probabilistic triggering, where
	only the head of the list is deterministically triggered and all the remaining items are
	probabilistically triggered.
However, their work does not consider contextual information, and it is also difficult to
	incorporate position discounts in a general triggering model.

@@

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains feedback information at all time $s < t$, as well as context information at time $t$. Each arm $a$ has a weight $\bw_t(a)$, representing the "quality" to the user at time $t$. Given history $\cH_t$, we assume that $\bw_{t,a}$'s are mutually independent random variables with expectation
\begin{equation} % eq:expectation
\label{eq:expectation}
\EE[\bw_{t}(a) | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. Define by $w_{t,a} = \theta_{\ast}^{\top} x_{t,a}$ the expected weight of base arm $a$ at time $t$. We assume that each $\bw_{t}(a)$ is a random variable with $R$-sub-Gaussian tail, which means that for all $\lambda \in \RR$, 
$$
\EE[\exp(\lambda(\bw_{t}(a) - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(\lambda^2 R^2 / 2).
$$

@@

The reward function on round $t$ is an application dependent function. We assume the expected reward of action $A$ is a function $f(A,w)$ of {\it expected weights} $w = (w(a))_{a \in E} \in [0,1]^{E}$ (at time $t$, $w = (w_t(a))_{a \in E}$) and satisfies the following two assumptions.

@@

The assumption of Lipschitz continuity gives an estimate of changes in reward function. To obtain a good estimation of reward function, the position $k$ with large discount value $\gamma_k$ needs a good estimation of $w(a_k)$. This means the positions with large discount $\gamma_k$ are more important to the reward function. For example in website recommendations, the learning agent will receive highest reward if the user selects the first item, so the first position is most important.

\wei{"large discount is more important" sounds weird. Usually large discount means cheaper and less
	important products. 
Perhaps we should seriously consider not using "position discount". It is a position weight, but
since weight is already used, we should call it something else. Perhaps "position factor"? 	
}
\shuai{What if I change this part by 'large $\gamma_k$'?}

@@

The $\alpha$-regret of action $A$ on time $t$ is
$$
R(t, A) = \alpha f_t^{\ast} - f(A, w_t),
$$
where $f_t^{\ast} = f(A_t^*, w_t)$ and $A_t^* = \argmax_{A\in\cS} f(A, w_t)$. Our goal is to minimize the cumulative (pseudo-)regret
$$
R(n) = \sum_{t=1}^n R(t, \bA_t).
$$

\wei{I think just writing $f(A,w_t)$ misses the context part. 
	$f$ as such defined is only a function of action $A$ and expected reward $w$, the subscript $t$
	is part of $w_t$, so is not an effective parameter. 
	We may need to explicitly write context into $f$, such as
	$f(A, w_t, x_t)$. 
	}

\wei{About approximation ratio $\alpha$: Do we have an example with an approximation oracle? 
	If not, we could remove it.
	It is also ok to keep it, but then in Theorems, like Theorem 4.3, we should say 
	$\alpha$-regret.
}

\shuai{There is no experiment with an approximation oracle. But if we want to add some experiment beyond our setting, maybe we can keep it.}

@@

\begin{algorithm} %C^3-UCB algorithm
	\caption{C$^3$-UCB}
	\label{alg:ConComCascade}
	\begin{algorithmic}[1]
		\STATE {Parameters:}
		\STATE {\qquad $\gamma_k\in[0,1], k \leq K; \delta > 0; \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
		\STATE {Initialization:}
		\STATE {\qquad $\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}

@@

At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent chooses her action. By Equation \eqref{eq:expectation}, we have 
$$
  \EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
  \{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
  \hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
  \bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a symmetric positive definite matrix. For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$. Next we build on a good estimate of the difference between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, which states the following results.

@@

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R(n) &\le \frac{\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(R\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right).
	\end{align}
\end{theorem}
\begin{proof} [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging for two reasons. First, our setting has contextual information. Second, we consider position discounts $\gamma_k, k \leq K$.

	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. Then by monotonicity and Lipschitz continuity, we have
	$$
		R(t, \bA_t) \leq B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
	$$
	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following deduction.
	\begin{align*}
    	&\EE[R(t, \bA_t)|\cH_t] \\
    	&\qquad = \EE \left[ \left. R(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
    \end{align*}
    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next Lemma solves this issue.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right),
    	$$
    \end{lemma}
    Then we can prove this theorem.
\end{proof}

@@

In the problem of network transportations or sequential task processing, $p^*$ defined above might be very small. So we have the following improvements. Suppose we also consider position discount here.  
\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$. Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regret of our algorithm, C$^3$-UCB for the conjunctive objective, satisfies
	\begin{align}
		R(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln \left( \frac{1 + C_\gamma n/(\lambda d)}{\delta^{2/d}}\right) } + \sqrt{\lambda}\right) \nonumber \\
		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln \left(\frac{C_\gamma n}{\delta^{2/d}}\right) \right)
	\end{align}
	where $f^* = \min_{t} f_t^{\ast}$.
\end{theorem}
\begin{proof}
	We will prove it in the appendix. The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first. And then use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}

>>>>

% my settings
\usepackage{amsmath}\allowdisplaybreaks
\usepackage{amssymb,amsfonts,bbm}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{empheq}
\usepackage{algorithm,algorithmic}
\usepackage{multirow}
\usepackage{ifthen}
\usepackage[usenames]{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{epstopdf}
%\usepackage{epsfig}
%\usepackage{times}
%\usepackage{helvet}
%\usepackage{courier}
%\usepackage{graphicx,subfigure}
%\usepackage{pdfpages}
%\usepackage{multirow}
%\usepackage{multicol}
\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\II}{\mathbb{I}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\bT}{\mathbb{T}}
\newcommand{\bOne}{\mathbbm{1}}
\newcommand{\bA}{\mathbf{A}}
\newcommand{\ba}{\mathbf{a}}
\newcommand{\bB}{\mathbf{B}}
\newcommand{\bO}{\mathbf{O}}
\newcommand{\br}{\mathbf{r}}
\newcommand{\bU}{\mathbf{U}}
\newcommand{\bV}{\mathbf{V}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bX}{\mathbf{X}}
\newcommand{\bY}{\mathbf{Y}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cH}{\mathcal{H}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\argmax}{\mathrm{argmax}}
\newcommand{\trace}{\mathrm{trace}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\norm}[1]{\| #1 \|}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{remark}[theorem]{Remark}
\newtheorem{proposition}[theorem]{Proposition}%[chapter]
\newtheorem{definition}[theorem]{Definition}%[chapter]
\newtheorem{corollary}[theorem]{Corollary}%[chapter]
\newtheorem{lemma}[theorem]{Lemma}%[chapter]
\newtheorem{example}[theorem]{Example}
\newenvironment{proof}{\noindent {\textbf{Proof. }}}{$\Box$ \medskip}

\newcommand{\CLemmaPrefixExi}{
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
	$$
	p_{t, B} \geq \frac{1}{2}f_{t}^{\ast} - 1 + \gamma_{\abs{B}}, \qquad R(t, B) \geq \frac{1}{2} R(t, A).
	$$ 
}
\newcommand{\CEqDeltaEstAnd}{
	$$
	\EE [R(t, \bA_t) |\cH_t ] \leq \frac{8}{f^{\ast}} \EE \left[ \bbeta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}} | \cH_t\right].
	$$
}
\newcommand{\CLemmaSumXiEstimateInDet}{
  If $\lambda \geq C_\gamma$, then
  $$
    \sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln \left(\frac{\det(\bV_t)}{\lambda^d} \right).
  $$
}
\newcommand{\CLemmaDetVt}{
  $\det(\bV_t)$ is increasing with respect to $t$ and 
  $$
    \det(\bV_t) \leq (\lambda + C_\gamma t/d)^d.
  $$
}

@@

%Putting context, position discounts, and generalized reward function together, we call our learning model the {\it contextual combinatorial cascading bandits}. We formally define this model, provide a complete algorithm and its regret analysis, and conduct experiments on both synthetic and real-world recommendation and network routing datasets to validate our approach.

%The main contributions of this paper can be summarized as follows: (1) we propose a general framework  that incorporates contextual information, position discounts, and general reward function to cover many real-world application scenarios; (2) we propose $C^3$-UCB, an efficient algorithm for contextual combinatorial cascading bandit, with regret bound as $\tilde{O}(\sqrt{n})$ for $n$ rounds; (3) we evaluate this algorithm on synthetic and real-world datasets and the results show that our algorithm effectively incorporates contextual information and position discounts with significant performance gains.

The organization of this paper is as follows: section 2 compares our work with previous works; section 3 presents the formulation of {\it contextual combinatorial cascading bandits} problem with general reward function and position discounts; section 4 gives our algorithm and main results both on general reward fucntions and two special reward functions; section 5 demonstrates the experimental results; and section 6 gives a final conclusion.

%\wei{The last two paragraphs have some repetition. Is there any technical part in the algorithm and analysis that we would like to mention in the introduction? So far the intro is only about conceptual additions to the model, and nothing about technical challenges and our solution. It is ok if conceptual contribution is what we want to emphasize, but if there is any technical contribution we can say, we can also say it here.}

%\shuai{Our proofs build on previous work but also generalize their proof in our setting. Two challenges have been dealt with, partial observability on contextual bandits and general reward function with position discounts.  }

@@

@@

The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference comes first) has a better performance than in decreasing order of their UCBs.
This unnatural result is perhaps because the order of items does not affect the reward and thus
	putting low preference items first and high preference items last may result in more feedbacks
	in the cascade.
The position discounts introduced in this paper forces the recommended set in the decreasing order 
	of UCBs, which is more realistic.
The work of \cite{combes2015learning} considered a similar cascading model to that of \cite{kveton2015cascading} with a particular case of contextual information, where at each time step, the category, which the user belongs to, is known and the user is recommended with $K$ items from a user-related group of items. Under this setting, they considered position discounts.
In our setting, users and items are represented by general feature vectors.

Our work considers contextual combinatorial bandits with cascading feedback and nonlinear reward. The paper \cite{li2010contextual} studied multi-armed bandit with context information, which recommends one item a time. A recent work \cite{qin2014contextual} (refered to as 'C$^2$UCB' in Table \ref{table:outline}) introduced contextual combinatorial bandit with semi-bandit feedback and nonlinear reward. Their feedback is more informative than ours. We relax the feedback from semi-bandit to cascading, yet our algorithm achieves the same order of regret bound.

@@

\citet{chen2015combinatorial} consider general reward functions and probabilistic triggering of base arms
	in the  stochastic combinatorial semi-bandit model (refered to as 'CUCB' in Table \ref{table:outline}).
Cascading bandits can be viewed as a particular type of probabilistic triggering, where
	only the head of the list is deterministically triggered and all the remaining items are
	probabilistically triggered.
However, their work does not consider contextual information, and it is also difficult to
	incorporate position discounts in a general triggering model.

@@

Let $\cH_t$ denote the history before the learning agent chooses action at time $t$. Thus $\cH_t$ contains feedback information at all time $s < t$, as well as context information at time $t$. Each arm $a$ has a weight $\bw_t(a)$, representing the "quality" to the user at time $t$. Given history $\cH_t$, we assume that $\bw_{t,a}$'s are mutually independent random variables with expectation
\begin{equation} % eq:expectation
\label{eq:expectation}
\EE[\bw_{t}(a) | \cH_t] = \theta_{\ast}^{\top} x_{t,a},
\end{equation}
where $\theta_{\ast}$ is an unknown $d$-dimensional vector with the assumption that $\norm{\theta_{\ast}}_2 \leq 1$ and $0 \leq \theta_{\ast}^{\top} x_{t,a} \leq 1$ for all $t, a$. Denote by 
$$
w_{t,a} = \theta_{\ast}^{\top} x_{t,a}
$$
the expected weight of base arm $a$ at time $t$. We assume that each $\bw_{t}(a)$ is a random variable with $R$-sub-Gaussian tail, which means that for all $\lambda \in \RR$, 
$$
\EE[\exp(\lambda(\bw_{t}(a) - \theta_{\ast}^{\top} x_{t,a})) | \cH_t] \leq \exp(\lambda^2 R^2 / 2).
$$

@@

The reward function on round $t$ is an application dependent function. We assume the expected reward of action $A$ is a function $f(A,w)$ of {\it expected weights} $w = (w(a))_{a \in E} \in [0,1]^{E}$ (at time $t$, $w = (w_t(a))_{a \in E} = (\theta_{\ast}x_{t,a})_{a \in E}) $ and satisfies the following two assumptions.

@@

The assumption of Lipschitz continuity gives an estimate of changes in reward function. To obtain a good estimation of reward function, the position $k$ with large $\gamma_k$ needs a good estimation of $w(a_k)$. This means the positions with large $\gamma_k$ are more important to the reward function. For example in website recommendations, the learning agent will receive highest reward if the user selects the first item, so the first position is most important.

@@

The $\alpha$-regret of action $A$ on time $t$ is
$$
R^{\alpha}(t, A) = \alpha f_t^{\ast} - f(A, w_t),
$$
where $f_t^{\ast} = f(A_t^*, w_t)$, $A_t^* = \argmax_{A\in\cS} f(A, w_t)$ and $w_t = (\theta_{\ast}^{\top}x_{t,a})_{a \in E}$. Our goal is to minimize the $\alpha$-regret
$$
R^{\alpha}(n) = \EE[ \sum_{t=1}^n R^{\alpha}(t, \bA_t)].
$$

@@

\begin{algorithm} %C^3-UCB algorithm
	\caption{C$^3$-UCB}
	\label{alg:ConComCascade}
	\begin{algorithmic}[1]
		\STATE {Parameters:}
		\STATE {\qquad $\{\gamma_k \in [0,1]\}_{k\leq K}; \delta = \frac{1}{\sqrt{n}}; \lambda \geq C_\gamma = \sum_{k=1}^{K} \gamma_k^2$}
		\STATE {Initialization:}
		\STATE {\qquad $\hat{\theta}_0 = 0, \bbeta_0(\delta) = 1, \bV_0 = \lambda I, \bX_0=\emptyset, \bY_0=\emptyset$}

@@

%At time $t$, we denote $\EE_t[\cdot] = \EE[\cdot | \cH_t]$, where $\cH_t$ is the history a time $t$ before the learning agent chooses her action.

By Equation \eqref{eq:expectation}, we have 
$$
  \EE[(\gamma_k \bw_{s,\ba_k^s}) | \cH_{s}] = \theta_*^{\top} (\gamma_k x_{s,\ba_k^s}).
$$
Using the ridge regression of data 
$$
  \{(\gamma_k x_{s,\ba_k^s}, \gamma_k \bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]},
$$
we get an $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
  \hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t,
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
  \bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a symmetric positive definite matrix. For any symmetric positive definite matrix $V \in \RR^{d \times d} $ and any vector $x \in \RR^{d \times 1}$, we define the $2$-norm of $x$ based on $V$ to be $\norm{x}_V = (x^{\top} V x)^{\frac{1}{2}}$. Next we build on a good estimate of the difference between $\hat{\theta}_t$ and $\theta_*$ by Theorem 2 in \cite{abbasi2011improved}, which states the following results.

@@

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and Lipschitz continuity with bound $B$. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&\qquad \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) \nonumber \\
		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln(C_\gamma n) \right),
	\end{align}
	where $R$ is the sub-Gaussian constant and $C_{\gamma} = \sum_{k=1}^K \gamma_k^2 \leq K$.
\end{theorem}
\begin{proof} [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging for two reasons. First, our setting has contextual information. Second, we consider position discounts $\gamma_k, k \leq K$.

	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. Then by monotonicity and Lipschitz continuity, we have
	$$
		R^{\alpha}(t, \bA_t) \leq B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
	$$
	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following deduction.
	\begin{align*}
    	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \\
    	&\qquad = \EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	&\qquad \leq \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    % &\EE_t[R_{\wedge}(t, \bA_t)] \\
    % &\qquad \EE \left[ \left. R_{\wedge}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{\wedge, t, \bA_t}} \bOne\{\bO_t\geq\abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right] \\
    \end{align*}
    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms. The next Lemma solves this issue.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right),
    	$$
    \end{lemma}
    Then we can prove this theorem.
\end{proof}

@@

In the problem of network transportations or sequential task processing, $p^*$ defined above might be very small. So we have the following improvements. Suppose we also consider position discount here.  
\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and $\gamma_K \geq 1 - \frac{1}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$. Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB for the conjunctive objective, satisfies
	\begin{align}
		R(n) \le& \frac{\sqrt{128}}{f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&\qquad \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) \nonumber \\
		=&O\left(\frac{d}{f^{\ast}}\sqrt{nK} \ln(C_\gamma n) \right).
	\end{align}
\end{theorem}
\begin{proof}
	We will prove it in the appendix. The main idea is that we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity first. And then use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}
